Wasted Money: Toronto Police Budget and Crime Number

### 2024-09-23 paper/paper.qmd
update

---
title: "Wasted Money: Toronto Police Budget and Crime Number"
subtitle: "Analyzing the changes in annual police budget and its effects
on the number of crimes within Toronto"
author: 
  - Yisu Hou
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Wasted Money: Toronto Police Budget and Crime Number"
subtitle: "Analyzing the changes in annual police budget and its effects
on the number of crimes within Toronto"
author: 
  - Yisu Hou
thanks: "Code and data supporting this analysis are available at: 
https://github.com/YisuHou1/Toronto-Police-Budget-Statistics."
date: today
date-format: long
abstract: "An analysis of Toronto's annual police budget and crime counts
was conducted to determine the effectiveness of the budget in preventing
crime within the city."
format: pdf
number-sections: true
bibliography: references.bib
---
